Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-18 paper/paper-v3.tex
a few typos

iven this sobering outcome with respect to the non-aggregated evaluation, 
we decided to ignore the clusters, and investigated whether parallels between the following cognitive principles could be observed: \basic, \contraposition, \abduction\ and \negFailure.
Table~\ref{tab:cogprinc} provides an overview of the predicted conclusions according to these principles.\footnote{Note that any advanced principle also includes the logic program clauses specified for \textsf{basic}.}
The predictions of the principles naturally raises a few questions on the plausibility of 
the underlying assumptions:
(i) Do participants use the same reasoning strategy throughout the same reasoning task, i.e.\ 
can their conclusions be 
explained by  the same principles throughout the whole reasoning task, or do they switch strategies within one reasoning task?
(ii) Is the list of principles in Section~\ref{sect:representing} complete, i.e.\ can the conclusions of all reasoners be covered
 by these principles? and
(iii) Do participants learn, i.e.\ do they improve their logical ability (with respect to CL) by doing the same reasoning task again?
We address these questions in the following.

>>>>

Given this sobering outcome with respect to the non-aggregated evaluation, 
we decided to ignore the clusters, and investigated whether parallels between the following cognitive principles could be observed: \basic, \contraposition, \abduction\ and \negFailure.
Table~\ref{tab:cogprinc} provides an overview of the predicted conclusions according to these principles.\footnote{Note that any advanced principle also includes the logic program clauses specified for \textsf{basic}.}
The predictions of the principles naturally raises a few questions on the plausibility of 
the underlying assumptions:
(i) Do participants use the same reasoning strategy throughout the same reasoning task, i.e.\ 
can their conclusions be 
explained by  the same principles throughout the whole reasoning task, or do they switch strategies within one reasoning task?
(ii) Is the list of principles in Section~\ref{sect:representing} complete, i.e.\ can the conclusions of all reasoners be covered
 by these principles? and
(iii) Do participants learn, i.e.\ do they improve their logical ability (with respect to CL) by doing the same reasoning task again?
We address these questions in the following.
